\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-03-23 papers/jss/article.Rnw
also 'R CMD Stangle' to create single R file with code -- is that what they ask for?
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@878 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

%% DE: I tend to have wider option(width=...) so this
%%     guarantees better line breaks
<<echo=FALSE,print=FALSE>>=
## cf http://www.jstatsoft.org/style#q12
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE, digits=4)
@

>>>>

%% DE: I tend to have wider option(width=...) so this
%%     guarantees better line breaks
<<echo=FALSE,print=FALSE>>=
## cf http://www.jstatsoft.org/style#q12
options(prompt = "R> ", 
        continue = "+  ", 
        width = 70, 
        useFancyQuotes = FALSE, 
        digits = 4)
@
